\documentclass[11pt]{article}

% Language setting
\usepackage[english]{babel}
\usepackage[toc,page]{appendix}

% Set page size and margins
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Packages
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{setspace}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, decorations.pathreplacing}

\usepackage[
    style=authoryear,
    backend=biber,
    natbib=true,
    maxcitenames=2,
    uniquelist=false,
    doi=false,
    isbn=false,
    url=false
]{biblatex}

\addbibresource{references.bib}
\usepackage{csquotes}

\DeclareMathOperator{\E}{\mathbb{E}}
% Theorem environments
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

% Spacing
\onehalfspacing
% \setlength\parindent{0pt}

% Custom commands
\newcommand{\R}{\mathbb{R}}
\newcommand{\mf}{m^{f}}
\newcommand{\md}{m^{d}}
\newcommand{\Mf}{M^{f}}
\newcommand{\Rstar}{R^{*}}

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{1.5cm} % Top padding

        \renewcommand*{\thefootnote}{\fnsymbol{footnote}}

        
        % Main Title
        {\LARGE \bfseries Fragile Economies: A General Equilibrium Model of Partial Default with a Banking Sector \par}
        
        \vspace{1.5cm}
        
        % Author (using small caps)
        {\large \textsc{Sam Blundell}\footnote{{I would like to thank Dimitrios Tsomocos and Fatih Kansoy for their invaluable supervision, and Udara Peiris for his countless advice and guidance.}} \par}
        \vspace{0.2cm}
        
        % Institution & Degree (using small caps)
        {\large \textsc{University of Oxford} \par}
        \vspace{0.2cm}
        {\large \textsc{MPhil Thesis in Economics} \par}
        
        \vspace{1cm}
        
        % Date (using small caps)
        {\normalsize \textsc{This Version:} \today \par}

        \renewcommand*{\thefootnote}{\arabic{footnote}}
        \setcounter{footnote}{0}
    \end{center}

\vspace{1cm}

% Abstract Section
\begin{abstract}
     Whilst examination of historical evidence following the 2008 financial crisis demonstrated the often antecedental role of domestic banking crisis in periods of sovereign default, much of the discussion on the so-called sovereign-bank diabolical loop posits an opposing mechanism, where a banking crisis is induced by the erosion of bank balance sheets through sovereign debt holdings. I propose a two-period general equilibrium model of partial default in which idiosyncratic banking-sector risk propagates through a costly state verification friction. I show that the real costs of default increase nonlinearly in financial fragility, generating import compression via higher external finance premia. Partial default is central to this mechanism, with larger haircuts amplifying the pass-through from sovereign default to intermediary net worth, import prices, and decreased consumption. Over-borrowing precedes these episodes, driven by a pecuniary externality in debt issuance: the sovereign fails to internalise how its borrowing impacts the price of borrowing. The model is calibrated to Sri Lanka's 2021–22 default.
    
    \vspace{1cm} % Space between abstract text and keywords
    
    % Keywords and JEL Codes
    \noindent\textbf{Keywords:} Debt, Renegotiation, Open economy, Banking sector, Costly State Verification, Sovereign-Bank Nexus, Sri Lanka. \\[0.2cm]
    \textbf{JEL Classification:} F34, F41, G21, G28
\end{abstract}
  


\clearpage
\end{titlepage}

\tableofcontents

\newpage


%========================================================================
\section{Introduction} \label{sec:intro}
%========================================================================

% Key stylized facts:
% Reinhart and Rogof (2011):
%   - As the larger emerging markets developed a financial sector in the late       1800s, these economies joined the serial-banking-crisis club.
%    - Ahead of banking crises, private debts (external debt, broader private       capital inflows, domestic bank debt) also display a repeated cycle of boom      and bust—the run-up in debts accelerates as the crisis nears
%   - the pattern of borrowing ahead of banking crises is NONLINEAR
%   - for the 22 advanced economies in our sample over the decade leading to        the global financial crisis which began with the subprime debacle in the        United States in 2007. In effect, the average external debt/GDP ratio           doubles during this period.
%   - Banking crises most often either PRECEDE or coincide with sovereign debt crises.

% The issue of "temporal precedence"

The experiences of Iceland in 2008 and Turkey in 2018 underscore the often antecedental nature of banking crises in periods of sovereign default. The co-movement of domestic bank CDS and sovereign spreads is a well-documented relationship \citep{acharya_pyrrhic_2014}, yet existing literature on the "doom loop" relationship between banks and sovereigns fails to rationalise the empirical regularity that, across history, banking crises more often than not induce sovereign default, rather than the inverse \citep{reinhart_financial_2011}. Public debt rises by roughly 86 percent in the three years following a banking crisis. These patterns are especially salient for emerging economies, where the development of domestic financial sectors has historically coincided with the emergence of serial default.

% OPPOSING VIEW - sovereign default induced bank-crisis
% Brunnermeier et al, 2016
%   - In Greece, Ireland, Italy, Portugal, and Spain,     the deterioration of sovereign creditworthiness     reduced the market value of banks’ holdings of      domestic sovereign debt
%   - We show that a “sunspot-driven” repricing of the country’s sovereign risk can result in bailouts of banks or other systemic financial institutions, which can lead to sovereign default when the primary surplus turns out to be low. In the absence of such repricing, the government never defaults. Effectively, the sunspot acts as a selection device among two equilibria.
%   - When observing sun-spot, investors under rationale expectations believe that 
%   - Proposition 1: (i) To avoid the diabolic loop, the ratio of bank equity to sovereign exposure must be at least ... (ii) The maximum amount of safe assets available to banks is ... Equivalently, ... is the minimum ratio of aggregate bank equity to sovereign exposure.

% Fahri and Triole, 2017:
%   -As banks use sovereign bonds as a store of value, holding them until they need the resources to invest, the solvency of the Sovereign is reduced for two reasons when the economy suffers an adverse shock. First, there is a direct negative effect of the shock on economic activity, and thus on the fiscal revenues of the Sovereign. Secondly, there is an indirect effect of the shock that operates through the balance sheets of banks. The initial fall in the price of public debt hurts the net worth of banks and thus their investment. If the Sovereign attaches a sufficiently high value to investment, it bails out the banks.

The dominant approach to modelling the sovereign-bank nexus relies upon the assumption that sovereign distress is the originating shock. \citet{brunnermeier_sovereign-bank_2016} utilise a sunspot to select an equilibrium that devalues sovereign bonds, prompting investors to anticipate, correctly, the erosion of bank balance sheets that hold sovereign debt. Building upon this mechanism, \citet{farhi_deadly_2018}'s model uses an aggregate-demand shock that induces sovereign default, followed by a bailout of the subsequently damaged balanced sheets of domestic banks, conditional on the level of oversight the sovereign has over these banks. \citet{bocola_pass-through_2016} demonstrates this transmission quantitatively, showing that elevated sovereign default risk raises domestic bank funding costs and contracts private lending. These existing models of the sovereign-bank nexus typically emphasise how sovereign distress weakens domestic banks through their sovereign bond holdings. Less attention has been paid to how the structure of the domestic banking system shapes the sovereign’s default problem itself. In particular, in the context of a domestic banking system that intermediates the real economy, the size of a haircut affects not only repayment and bank-net worth but also external finance premia, import prices, and consumption. This thesis studies this \textit{intensive margin} of sovereign default.
% MY MODEL:
%   - home bias/financial repression induced holdings of sovereign bonds (as a single risky asset)
%   - Bank insolvency brought on by idiosyncratic shock rather than aggregate -> the level of insolvency maps on to default cost
%   - we can think of the cost of default increasing as brought about by the real economic costs of a contraction of banks from their intermediation in the real economy; in lending, issuance activity etc.
% aggregate shocks bring about larger haircuts

This thesis provides a theoretical grounding for the channels in which domestic banking fragility shapes the real costs and equilibrium severity of sovereign default. It does so whilst rationalising key stylised facts that remain empirical regularities:

\begin{enumerate}[label=(\roman*)]
    \item Default is associated with a deep recession in GDP and consumption \citep{yeyati_elusive_2011};
    \item Prior to defaulting episodes, there is typically a large, non-linear increase in external debt as a share of GDP \citep{reinhart_financial_2011};
    \item The output costs associated with default are amplified in the banking sector's exposure to domestic sovereign debt \citep{sosa-padilla_sovereign_2018};
    \item Larger partial defaults (haircuts) co-move with higher sovereign spreads, higher debt, and lower output \citep{arellano_partial_2023}.
\end{enumerate}

Although the mechanism is not specific to emerging economies, the thesis focuses on this group because the model’s assumptions are especially salient in this setting. Emerging economies are more exposed to financial market fragility \citep{fostel_leverage_2008} and banking crises \citep{kaminsky_twin_1999, deghi_sovereign-bank_2022}, and domestic banks frequently hold large quantities of sovereign debt \citep{gennaioli_sovereign_2014}, making them ideal candidates to study in a small open-economy setting.

My framework consists of two periods, zero and one, with a small open economy populated by three agent types: a sovereign, a continuum of domestic banks and an international investor. The setup adopts the strategic-default framework of \citet{eaton_debt_1981}, with the sovereign choosing default after observing the period-one state and lacking commitment to repay, but with two key departures: default is continuous (partial) rather than binary, and the cost of default arises endogenously through the financial sector rather than as an exogenous output loss. In period zero, the sovereign issues bonds that mature at period one, which both the banks and the international investor purchase. This bond is risky, and is priced accordingly by the risk-neutral investor, who anticipates that in period one the sovereign will choose what proportion of its outstanding debt to default upon. Partial default erodes the net-worth of the banks via their domestic bond holdings. A representative household consumes an aggregate of home and foreign goods with limited substitutability, and it is the household, acting as the sovereign, that determines both borrowing in period zero and default in period one. The household's period-zero borrowing decision is subject to a pecuniary externality, following \citet{goodhart_debt_2018}: atomistic households take the bond price as given and do not internalise how their collective borrowing depresses it, generating overborrowing relative to a constrained-efficient benchmark and elevating the debt levels at which default becomes severe. The domestic banks intermediate these foreign goods, for which they borrow intra-period working capital from the international lender to purchase. Crucially, the banks are subject to idiosyncratic risk in this intermediated goods market; as it is costly for the international lender to observe the state of the banks (costly-state verification, henceforth CSV), this risk raises the external finance premium charged on these working capital loans. This higher premium is passed on to the household via the price of imported goods and depresses household consumption. The idiosyncratic risk steepens the import-price function in default, as the convex CSV penalty becomes more sensitive to net-worth erosion when the financial friction is severe. Banking fragility therefore raises the marginal real cost of default and amplifies the output and import-compression consequences conditional on any realised haircut. Beyond this contribution on financial fragility, the model delivers a constrained-inefficiency result: under partial default, the atomistic household over-borrows, generating a role for macroprudential intervention through capital-flow taxes or borrowing limits.

The remainder of the thesis proceeds as follows. Sections~\ref{sec:environment}--\ref{sec:agents} set out the model environment and the three agents populating the economy. A sequence of events is available in Section \ref{sec:timings}. Section~\ref{sec:equilibrium} defines the competitive equilibrium and establishes nominal neutrality, allowing the analysis to proceed in real terms. Section~\ref{sec:optimality} derives the model's optimality conditions, focusing on the transmission of sovereign default to import prices through intermediary balance sheets, and Section~\ref{sec:chareq} characterises the resulting Period~0 and Period~1 equilibria. Section~\ref{sec:implications} introduces a constrained Ramsey planner as a normative benchmark, establishing an over-borrowing result relative to this benchmark, and tracing the model's key comparative statics in idiosyncratic banking risk and the share of sovereign debt held domestically. Section~\ref{sec:quantitative} simulates the model, utilising Sri Lanka's 2021--22 default episode as a calibration anchor, and Section~\ref{sec:discussion} develops resulting testable predictions and concludes.

% Literature Review
%   - Douglas Diamond and Philip Dybvig’s (1983):       offers seminal view that short-term illiquid        asset holdings are vulnerable to "confidence        runs"
%   - mulitple-equilibriia models: Sachs (1984)...      "Unfortunately, multiple equilibria models have     their limitations. Absent a model of the            underlying sunspots, it is difficult to assess      the degree of risk across different                 economies... senstive to difficult-to-confirm       assumptions".

% Bias: 
%   - For example, Alberto Alesina and Guido Tabellini (1990) as well as Torsten Persson and Lars E. O. Svensson (1989) develop models where incumbents tend to run large deficits essentially because the temporary nature of their term in office raises their effective discount rate.
%   ^ This can broadly be interpretted as a coordination failiure, as in The Greek Dilemma

% Fostel, Ana, and John Geanakoplos. 2008. “Leverage Cycles and the Anxious Economy.” American Economic Review, 98(4): 1211–44. ??

% Leonello (2018), which I mentioned in the citation list earlier, is explicitly bidirectional via bank runs feeding back into sovereign solvency through guarantees — and there the bank-side originating shock is a bank run, which is a coordination failure on the bank side, 

The approach posed within this thesis connects with a number of areas within the literature on sovereign default. It builds on the canonical sovereign default framework of \citet{eaton_debt_1981} and \citet{arellano_default_2008} where the sovereign lacks commitment in repayment of debt, following the realisation of an aggregate state. By endogenising the default penalty, the model connects closely to the work of \citet{mendoza_general_2012}, where imports and working-capital frictions are central to the real effects of default. In contrast to these approaches, however, my framework models default partially, as a continuous haircut, adhering to the observations of \citet{arellano_partial_2023} and building upon \citet{goodhart_debt_2018, peiris_capital_2025}. As discussed, this thesis connects to the sovereign-bank nexus literature, stemming from \citet{diamond_bank_1983}, including \citet{acharya_pyrrhic_2014, brunnermeier_sovereign-bank_2016, bocola_pass-through_2016, farhi_deadly_2018, gennaioli_sovereign_2014, sosa-padilla_sovereign_2018}, by showing how domestic bank exposure to sovereign debt shapes the marginal cost and macroeconomic consequences of partial default. Outside of the sovereign default literature, the costly-state verification framework follows \citet{bernanke_chapter_1999, christiano_risk_2014}, delivering a macroprudential overborrowing result through a pecuniary externality in debt issuance.

%========================================================================
\section{The Model Environment} \label{sec:environment}
%========================================================================

I present an endowment economy inhabited by three distinct agents: a representative household (the sovereign), a continuum of risk-neutral domestic import intermediaries (domestic banks) indexed by $i \in [0,1]$, and a risk-neutral international lender. The discrete-time model spans two periods, $t \in \{0,1\}$.

\subsection{The Economy}

The representative household has time-separable expected utility over consumption:
\begin{equation}\label{eq:V0}
V_0 = u(C_0) + \beta \, \E_0\bigl[u(C_1)\bigr],
\end{equation}
where $u$ is strictly increasing, strictly concave, and satisfies Inada conditions, and $\beta \in (0,1)$ is the subjective discount factor.

The household produces the final consumption good $C_t$ from domestic inputs $\md_t$ and foreign inputs $\mf_t$ via a CES aggregator:
\begin{equation}\label{eq:CES}
C_t = \bigl[\alpha (\md_t)^{\eta} + (1-\alpha)(\mf_t)^{\eta}\bigr]^{1/\eta}, \qquad t \in \{0,1\},
\end{equation}
where $\alpha \in (0,1)$ is the Armington weight on domestic inputs and $\eta < 0$ governs the elasticity of substitution $\sigma = 1/(1-\eta) \in (0,1)$. The restriction $\eta < 0$ ensures the two inputs are strict gross complements: the household cannot substitute away from foreign inputs to avoid punitive price increases.

The household receives a per-period endowment $y_t$ of domestic inputs. Period 1 endowment growth $g_1 \equiv y_1/y_0$ follows an AR(1) process in logs:
\begin{equation}\label{eq:endowgrowth}
\log(g_1) = (1-\rho)\log(\mu_g) + \rho \log(g_0) + \varepsilon, \qquad \varepsilon \sim \mathcal{N}(0, \sigma_g^2).
\end{equation}

There exists an exogenous risk-free gross world interest rate $R^*>1$. Following \citet{eaton_debt_1981}, the international lender has access to a frictionless world capital market at this rate. As such, the lender will only participate in lending activities, both interperiod and intraperiod, which guarantee them a rate of return at least as high as this market rate.

\subsection{Nominal Structure and Exchange Rate} \label{sec:nominal}
Let $P_t$ denote the domestic-currency price of domestic goods, and $e_t$ the exchange rate, expressed as units of domestic currency per unit of foreign currency. The real exchange rate is defined as
\begin{equation} \label{eq:real-exch}
    RER_t \equiv \frac{e_t}{P_t},
\end{equation}
where foreign input prices are normalised to one. I assume that bonds within the domestic economy are issued in real-terms, representing a fixed quantity of domestic output, as to ensure the real net-of-default payoff for the household is invariant to domestic price levels. \\

Domestic input purchases are subject to a cash-in-advance constraint that pins down domestic price levels:
\begin{equation} \label{eq:cash-in-advance}
    MS_t=P_t \cdot m^d_t,
\end{equation}
where $MS_t$ denotes the domestic money supply. \\

Proposition \ref{prop:neutrality} below establishes that, given neutrality assumptions, the real exchange rate reduces to $\bar{RER}=1$, with one unit of foreign input exchanging for one unit of domestic input on the (frictionless) world market. The remainder of the analysis proceeds in real terms.

\subsection{Financial Instruments and the CSV Friction}\label{sec:csv}

The household issues one-period, non-contingent bonds $b_1$ at price $q_0$ in Period 0. Each bond promises one unit of the domestic num\'{e}raire at maturity. A fraction $\gamma \in (0,1)$ of outstanding bonds is held by the domestic intermediary sector; the remainder $(1-\gamma)$ is held by the international lender. The parameter $\gamma$ is exogenous and institutional, reflecting a regulatory liquidity mandate requiring domestic banks to hold a fraction of outstanding sovereign bonds as eligible liquid assets. This captures the well-documented home bias in sovereign debt holdings across emerging market banking sectors \citep{gennaioli_sovereign_2014}. 

Upon realisation of the Period 1 endowment, the sovereign household chooses a continuous partial default $D \in [0, b_1]$, interpreted as a haircut on outstanding debt. As an important departure from \citet{arellano_default_2008}, the household does not internalise the effect of its default decision on the price of debt. Rather, default occurs in equilibrium as the household internalises the impact of default on import prices. The sovereign in this setting can be thought of as being subject to a coordination failure in the issuance of new debt \citep{goodhart_debt_2018}. \\

Following the risk-shock structure proposed by \citet{christiano_risk_2014}, each intermediary is subject to an idiosyncratic productivity shock $\omega_{i,t}$, drawn independently each period from a log-normal distribution with mean one and variance $\sigma_\omega^2$:
\begin{equation}\label{eq:omega_dist}
\log(\omega_{i,t}) \sim \mathcal{N}\!\left(-\tfrac{\sigma_\omega^2}{2},\, \sigma_\omega^2\right).
\end{equation}
Let $F(\omega)$ and $f(\omega)$ denote the CDF and PDF of this distribution. Because the realised shock is private information to the intermediary, the financial contract between the intermediary and the international lender is subject to a costly state verification (CSV) friction, following \citet{bernanke_chapter_1999}.

The CSV friction is characterised by two functions of the default threshold $\bar{\omega} \geq 0$ that appear throughout the analysis. The expected gross share of intermediary revenue accruing to the lender under the optimal debt contract is:
\begin{equation}\label{eq:Gammadef}
\Gamma(\bar{\omega}) \equiv \int_0^{\bar{\omega}} \omega \, dF(\omega) + \bar{\omega}\bigl[1 - F(\bar{\omega})\bigr],
\end{equation}
and the expected revenue share from defaulting intermediaries is:
\begin{equation}\label{eq:Gdef}
G(\bar{\omega}) \equiv \int_0^{\bar{\omega}} \omega \, dF(\omega),
\end{equation}
so that $\mu G(\bar{\omega})$ is the expected deadweight auditing cost, where $\mu \in (0,1)$ is the monitoring cost parameter. These functions satisfy $\Gamma(0) = 0$, $\Gamma'(\bar{\omega}) = 1 - F(\bar{\omega}) > 0$, and $G'(\bar{\omega}) = \bar{\omega} f(\bar{\omega}) \geq 0$. Under the log-normal specification \eqref{eq:omega_dist}, the derivatives admit the closed forms:
\begin{align}
\Gamma'(\bar{\omega}) &= 1 - \Phi\!\left(\frac{\ln(\bar{\omega}) + \sigma_\omega^2/2}{\sigma_\omega}\right), \label{eq:Gammaprime}\\[4pt]
\mu G'(\bar{\omega}) &= \frac{\mu}{\sigma_\omega}\,\varphi\!\left(\frac{\ln(\bar{\omega}) + \sigma_\omega^2/2}{\sigma_\omega}\right), \label{eq:muGprime} \\
\Gamma''(\bar{\omega}) &= -\frac{1}{\bar{\omega}\,\sigma_\omega}\,
\varphi\!\left(\frac{\ln\bar{\omega}
+ \sigma_\omega^2/2}{\sigma_\omega}\right), \label{eq:Gammapp}
\end{align}
where $\Phi$ and $\varphi$ denote the standard normal CDF and PDF. It is worth noting that $\Gamma''$ is strictly negative for all $\bar{\omega} > 0$. \\

The "risk shocks" introduced by $\sigma_{\omega}$ within the model capture the cross-sectional idiosyncratic risk in the banking sector, shown to be a dominant driver of US business-cycle fluctuations \citep{christiano_risk_2014}. This risk is the main point of fragility within the domestic banking sector from which the model's default premium propagates from, and is the subject of this thesis' main comparative statics in Section \ref{sec:comp_stat_sigma_omega}.


%========================================================================
\section{Agents} \label{sec:agents}
%========================================================================

\subsection{Domestic Household} \label{sec:household}

The representative household acts as both a consumer and a final-goods producer, aggregating domestic and foreign inputs via \eqref{eq:CES}. It takes the internal price of foreign inputs, $p_{m,t}$ - the relative price expressed in units of domestic inputs - as given in each period.

\paragraph{Period 0.} The household chooses domestic inputs $\md_0$, foreign inputs $\mf_0$, and bond issuance $b_1$ to maximise \eqref{eq:V0} subject to:
\begin{equation}\label{eq:bc0}
\md_0 + p_{m,0}\,\mf_0 = y_0 - b_0 + q_0 b_1 + \Pi_0,
\end{equation}
where $b_0$ denotes pre-existing debt obligations and $\Pi_t$ is a lump-sum dividend received from the domestic intermediary sector, defined below. The household acts as a price-taker in its own debt issuance.

\paragraph{Period 1.} After $y_1$ is realised, the household chooses default $D \in [0, b_1]$ and inputs $(\md_1, \mf_1)$ to solve:
\begin{equation}\label{eq:hh_p1}
\max_{D \in [0,b_1],\; \md_1 \geq 0,\; \mf_1 \geq 0} \; u(C_1),
\end{equation}
subject to:
\begin{equation}\label{eq:bc1}
\md_1 + p_{m,1}(D) \cdot \mf_1 = y_1 - (b_1 - D) + \Pi_1.
\end{equation}
The import price $p_{m,1}$ depends on $D$ through the intermediary balance sheet channel described below. In order for default to occur in equilibrium, the household must internalise this effect. Crucially, while the household internalises the dependence of $p_{m,1}$ on $D$, it treats the dividends $\Pi_0, \Pi_1$ as lump sums, that is, it does not internalise $\partial \Pi_t / \partial D$ when choosing default. This asymmetry reflects the fact that import prices are directly observable and contractually relevant to the household's purchasing decisions, whereas the dividend is a residual claim on aggregate intermediary surplus that the atomistic households do not perceive to depend on their own actions.

\subsection{Domestic Intermediaries}\label{sec:intermediary}

A continuum of ex-ante identical domestic intermediaries $i \in [0,1]$ operate in a perfectly competitive market with free entry and exit to intermediate foreign inputs $\mf$ in each period. Each intermediary purchases imports using a combination of its own net worth $n_{i,t}$ and working capital $\kappa_{i,t}$ borrowed from the international lender at gross intra-period rate $Z_{i,t}$, with repayment due within the same period. The intermediary's intra-period balance sheet is:
\begin{equation}\label{eq:balsheet}
 \mf_{i,t} = n_{i,t} + \kappa_{i,t}, \qquad t \in \{0,1\}.
\end{equation}
It is worth emphasising that $\kappa_{i,t}$ is an intra-period contract, with borrowing and repayment occuring within the same period $t$, distinct from the inter-period sovereign bond $b_1$ issued in Period 0 and maturing in Period 1. The international lender's opportunity cost is $\Rstar$ for both contracts, but the two markets clear independently.

The intermediary's net worth depends on the period and the sovereign's default choice:
\begin{align}
n_{i,0} &= \bar{n}(\gamma) + \gamma b_0 - \gamma q_0 b_1, \label{eq:nw0}\\
n_{i,1} &= \bar{n}(\gamma) + \gamma(b_1 - D). \label{eq:nw1}
\end{align}
The sovereign-independent component $\bar{n}(\gamma) > 0$ represents the intermediary sector's exogenous capitalisation. To distinguish the portfolio composition role of $\gamma$ from a mechanical balance-sheet size effect, ex-ante total intermediary assets at the start of Period 0 are $\gamma$-invariant:
\begin{equation}\label{eq:nbar_rescale}
\bar{n}(\gamma) + \gamma b_0 \;\equiv\; \bar{A},
\end{equation}
where $\bar{A}$ is a calibrated constant pinned down by the baseline values $(\bar{n}_{\text{base}}, \gamma)$ in Table~\ref{tab:calibration}. Holding $\bar{A}$ fixed when varying $\gamma$ ensures that comparative statics in $\gamma$ isolate how exposed banks are to sovereign risk, rather than how large their balance sheet is.

Before delivering inputs to the household, intermediary $i$ is subject to the idiosyncratic shock $\omega_{i,t}$, so that aggregate effective foreign inputs available for sale are:
\begin{equation}\label{eq:agg_supply}
\Mf_t = \int_0^1 \omega_{i,t}\,\mf_{i,t}\,di.
\end{equation}

The cutoff threshold $\bar{\omega}_{i,t}$ is the exact shock realisation at which the intermediary just breaks even:
\begin{equation}\label{eq:threshold}
\bar{\omega}_{i,t}\, p_{m,t}\, \mf_{i,t} = Z_{i,t}\,\kappa_{i,t} = Z_{i,t}\bigl( \mf_{i,t} - n_{i,t}\bigr).
\end{equation}
If $\omega_{i,t} \geq \bar{\omega}_{i,t}$, the intermediary repays in full and retains the surplus. If $\omega_{i,t} < \bar{\omega}_{i,t}$, the intermediary defaults; the lender pays the auditing cost, destroying a fraction $\mu$ of realised assets and recovering $(1-\mu)\omega_{i,t}\,p_{m,t}\,\mf_{i,t}$.

Each intermediary chooses $\mf_{i,t}$ to maximise expected profits:
\begin{equation}\label{eq:int_obj}
\max_{\mf_{i,t}} \; \bigl[1 - \Gamma(\bar{\omega}_{i,t})\bigr]\,p_{m,t}\,\mf_{i,t},
\end{equation}
yielding the first-order condition:
\begin{equation}\label{eq:int_foc}
\bigl[1 - \Gamma(\bar{\omega}_{i,t})\bigr]\,p_{m,t}\,\mf_{i,t} = \Gamma'(\bar{\omega}_{i,t})\,Z_{i,t}\,n_{i,t}.
\end{equation}
Unlike the bilateral optimal contract in \citet{christiano_risk_2014}, intermediaries here take $Z_{i,t}$ as given in a competitive credit market. They do not internalise the marginal auditing costs when choosing their scale of intermediation, generating a steeper external finance premium for a given level of net worth. This departure reflects the competitive and fragmented nature of the domestic banking sector.

\paragraph{Intermediary dividends.} All intermediaries are owned by the representative household, who acts as the residual claimant on any surplus they generate. Once the idiosyncratic shock is realised and obligations to the international lender are settled, solvent intermediaries distribute their surplus revenue as a lump-sum dividend. The per-unit surplus of intermediary $i$, net of working-capital repayment, is:
\begin{equation}\label{eq:pi_i}
\pi_{i,t} = \begin{cases} (\omega_{i,t} - \bar{\omega}_t)\,p_{m,t}\,\mf_{i,t} & \text{if } \omega_{i,t} \geq \bar{\omega}_t, \\ 0 & \text{otherwise}. \end{cases}
\end{equation}
Aggregating across the continuum of intermediaries and applying the law of large numbers:
\begin{equation}\label{eq:Pi_agg}
\Pi_t = \int_{\bar{\omega}_t}^{\infty} (\omega - \bar{\omega}_t)\,p_{m,t}\,\Mf_t\,dF(\omega) = \bigl[1 - \Gamma(\bar{\omega}_t)\bigr]\,p_{m,t}\,\Mf_t.
\end{equation}
This is the aggregate dividend $\Pi_t$ that enters the household's budget constraints \eqref{eq:bc0}--\eqref{eq:bc1}.

\subsection{International Lender} \label{sec:lender}

The international lender is risk-neutral, infinitely funded, and prices all contracts at the risk-free rate $\Rstar$.

\paragraph{Working capital market.} The lender's zero-profit participation constraint equates the expected payoff to the opportunity cost:
\begin{equation}\label{eq:lender_zp}
\left[\int_{\bar{\omega}_{i,t}}^{\infty} \bar{\omega}_{i,t}\,dF(\omega) + (1-\mu)\!\int_0^{\bar{\omega}_{i,t}} \omega\,dF(\omega)\right] p_{m,t}\,\mf_{i,t} = \Rstar \kappa_{i,t}.
\end{equation}
Using the CSV functions from \Cref{sec:csv}, this simplifies to:
\begin{equation}\label{eq:lender_zp_compact}
\bigl[\Gamma(\bar{\omega}_{i,t}) - \mu G(\bar{\omega}_{i,t})\bigr]\,p_{m,t}\,\mf_{i,t} = \Rstar\bigl( \mf_{i,t} - n_{i,t}\bigr).
\end{equation}

\paragraph{Intertemporal bond market.} The lender prices household debt at the risk-neutral expected recovery rate:
\begin{equation}\label{eq:bondprice}
q_0(y_0, b_1) = \frac{1}{\Rstar}\,\E_0\!\left[1 - \frac{D(y_1, b_1)}{b_1}\right].
\end{equation}

%========================================================================
\section{Sequence of Events} \label{sec:timings}
%========================================================================

The within-period timing of decisions, shock realisations, and settlements is set out below; Figure~\ref{fig:timeline} summarises the sequence diagrammatically.

\paragraph{Period 0:}
\begin{enumerate}[label=(\alph*), itemsep=2pt, topsep=4pt]
    \item The household receives the deterministic endowment $y_0$.
    \item The sovereign issues one-period bonds $b_1$ at the equilibrium price $q_0$; a fraction $\gamma$ is absorbed by domestic intermediaries, composing their pre-haircut Period 1 net worth, with the remaining $1-\gamma$ held by the international lender.
    \item Intermediaries borrow working capital $\kappa_0$ from the international lender under the CSV contract and use it to purchase foreign inputs $\mf_0$.
    \item Idiosyncratic productivity shocks $\omega_{i,0}$ are realised. Solvent intermediaries deliver inputs to the household and distribute the aggregate surplus $\Pi_0$; insolvent intermediaries are monitored at cost.
    \item The household produces and consumes $C_0$.
\end{enumerate}

\paragraph{Period 1:}
\begin{enumerate}[label=(\alph*), itemsep=2pt, topsep=4pt]
    \item The aggregate growth shock $g_1$ is realised, determining $y_1 = g_1 y_0$.
    \item The household chooses partial default $D \in [0, b_1]$; the resulting haircut on intermediaries' bond holdings pins down their Period 1 post-haircut net worth $n_1$.
    \item Conditional on $n_1$, intermediaries contract working capital $\kappa_1$ under the CSV contract, and the equilibrium external finance premium determines the domestic price of foreign inputs $p_{m,1}$.
    \item Idiosyncratic shocks $\omega_{i,1}$ are realised. Solvent intermediaries deliver inputs and distribute surplus $\Pi_1$; insolvent intermediaries are monitored at cost.
    \item The household produces and consumes $C_1$, and the non-defaulted portion $b_1 - D$ of sovereign debt is settled.
\end{enumerate}

\input{timeline}

%========================================================================
\section{Equilibrium Definitions} \label{sec:equilibrium}
%========================================================================

\subsection{Aggregation and Market Clearing}

Because all intermediaries are ex-ante identical, in any symmetric equilibrium they hold the same net worth ($n_{i,t} = N_t$), purchase the same raw imports ($\mf_{i,t} = \Mf_t$), borrow the same working capital ($\kappa_{i,t} = K_t$), and face the same default threshold ($\bar{\omega}_{i,t} = \bar{\omega}_t$). Henceforth all intermediary-level variables are written without the $i$ subscript.

Three markets must clear in equilibrium. The sovereign debt market requires that total issuance equals total demand:
\begin{equation}\label{eq:mc_debt}
b_1 = \gamma b_1 + (1-\gamma)b_1.
\end{equation}
The foreign inputs market requires that the household's demand for effective foreign inputs equals aggregate intermediary supply net of auditing losses:
\begin{equation}\label{eq:mc_foreign}
\mf_t = \Mf_t\bigl[1 - \mu G(\bar{\omega}_t)\bigr].
\end{equation}
The domestic inputs market clears by Walras' law given the first two conditions and the household budget constraint.

Aggregating across agents and imposing market clearing, the economy's balance-of-payments constraints are:
\begin{align}
\md_0 + \Rstar  \Mf_0 - (\Rstar - 1)N_0 &= y_0 + \bar{n} - (1-\gamma)(b_0 - q_0 b_1), \label{eq:bop0}\\
\md_1 + \Rstar  \Mf_1 - (\Rstar - 1)N_1 &= y_1 + \bar{n} - (1-\gamma)(b_1 - D). \label{eq:bop1}
\end{align}

\subsection{Equilibrium Definition}

\begin{definition}[Competitive Equilibrium]\label{def:equil}
Given initial debt $b_0$, long-run net worth $\bar{n}$, exogenous global parameter $R^*$ and realised aggregate endowments $(y_0, y_1)$, a competitive equilibrium is defined as a collection of prices $\{q_0,\, p_{m,0},\, p_{m,1},\, Z_0,\, Z_1\}$, thresholds $\{\bar{\omega}_0,\, \bar{\omega}_1\}$, and allocations $\{C_t,\, \md_t,\, \mf_t,\, \Mf_t,\, b_1,\, D,\, N_t,\, K_t,\, \Pi_t\}_{t=0,1}$ such that:
\begin{enumerate}[label=(\roman*)]
\item The representative household optimises lifetime utility, choosing $(\md_t, \mf_t, b_1, D)$ given prices $(q_0, p_{m,0}, p_{m,1})$;
\item Each domestic intermediary selects $\mf_{i,t}$ to maximise expected profit \eqref{eq:int_obj}, given the lending rate $Z_t$;
\item The international lender prices sovereign bonds via \eqref{eq:bondprice} and the working capital zero-profit condition \eqref{eq:lender_zp_compact} holds;
\item The sovereign debt, foreign input, and domestic input markets clear;
\item Net worth satisfies \eqref{eq:nw0}--\eqref{eq:nw1}, working capital is consistent: $K_t =  \Mf_t - N_t$, and aggregate dividends satisfy \eqref{eq:Pi_agg}.
\end{enumerate}
\end{definition}

\subsection{Nominal Neutrality}

Under the nominal structure defined in Section \ref{sec:nominal}, the following result establishes that the real equilibrium is self-contained:

\begin{lemma}[Nominal Neutrality]\label{prop:neutrality}
Suppose that:
\begin{enumerate}[label=(\roman*)]
    \item sovereign bonds are denominated in units of the domestic good, so that the real payoff $(b_1 - D)$ is independent of $P_t$;
    \item domestic goods prices are fully flexible; and
    \item the real exchange rate is constant: $RER_t = \bar{RER}$ for all $t$.
\end{enumerate}
Then the real allocation $\{C_t,\, m^d_t,\, m^f_t,\, M^f_t,\, b_1,\, D,\, \bar{\omega}_t,\, Z_t,\, \Pi_t\}_{t=0,1}$ and the real prices \\
$\{q_0,\, p_{m,0},\, p_{m,1}\}$ are determined by the system of equations \emph{\eqref{eq:CES}}--\emph{\eqref{eq:euler}}  independently of the domestic money supply $MS_t$, the nominal exchange rate $e_t$, and the domestic price level $P_t$. The nominal variables are determined residually by:
\begin{equation}\label{eq:price-level}
    P_t = \frac{MS_t}{m^d_t}, \qquad e_t = P_t \cdot \bar{RER},
\end{equation}
where $\bar{RER} = 1$.
\end{lemma}

\begin{proof}
Express each agent's budget constraint and optimality condition in nominal terms, then deflate by $P_t$. The household's Period 1 nominal budget
constraint is
\begin{equation*}
    P_1 \cdot m^d_1 + P^{\text{nom}}_{m,1} \cdot m^f_1
    = P_1 \cdot y_1 - P_1 \cdot (b_1 - D) + P_1 \cdot \Pi_1,
\end{equation*}
where $P^{\text{nom}}_{m,1}$ is the nominal domestic-currency price of foreign inputs. Dividing by $P_1$ and letting $p_{m,1} \equiv P^{\text{nom}}_{m,1}/P_1$ recovers \eqref{eq:bc1}. The relative price $p_{m,t}$ thus captures the full real cost of foreign inputs to the domestic household, inclusive of both the underlying terms of trade and the friction-based markup, detailed in Section \ref{sec:csv}. 

The same exercise can be conducted for Period 0 equilibrium, recovering the stated real system by deflation as above.

The intermediary balance sheet in nominal terms is $e_t \cdot m^f_{i,t} = P_t \cdot n_{i,t} + e_t \cdot \kappa_{i,t}$. Dividing by $P_t$ and noting $e_t/P_t = 1$ under assumption (iii) yields \eqref{eq:balsheet}.

The CSV functions $\Gamma(\bar{\omega})$ and $G(\bar{\omega})$ are unit-free ratios, so the threshold condition \eqref{eq:threshold}, the lender's zero-profit condition \eqref{eq:lender_zp}, and the import price equation \eqref{eq:pm} are invariant to the choice of num\'{e}raire.

Since every equilibrium condition in the real system is recovered by deflation, the real allocation is independent of $MS_t$. Given the equilibrium values of $m^d_t$, the price level follows from (\ref{eq:cash-in-advance}) and the nominal exchange rate from (\ref{eq:price-level}).

\end{proof}

Let $i_t$ denote the domestic nominal interest rate. Under satisfaction of the uncovered interest rate parity condition, the nominal rate can be expressed as
\begin{equation}
    (1+i_t)=R^*\E_t\left[\frac{e_{t+1}}{e_t}\right].
\end{equation}

Under the assumption of nominal neutrality, with domestic prices being pinned down by \eqref{eq:cash-in-advance}, this becomes
\begin{equation}
    (1+i_t)=R^*\E_t\left[\frac{MS_{t+1}/m^d_{t+1}}{MS_t/m^d_t}\right].
\end{equation}
The domestic nominal rate therefore depends on monetary policy and the real allocation of domestic inputs, but is determined residually and does not feed back into the real equilibrium.

Following the Fisher equation, the domestic real interest rate $R_t$ is expressed as
\begin{equation}
    R_t=(1+i_t)\frac{P_t}{\E_t[P_{t+1}]}=R^*,
\end{equation}
with the domestic rate equalising each period to the time-invariant world gross rate $R^*$.



%========================================================================
\section{Optimality Conditions} \label{sec:optimality}
%========================================================================

\subsection{The Financial Friction}

Three key relationships emerge from the intermediary and lender optimality conditions. Aggregating across intermediaries and dividing the threshold condition \eqref{eq:threshold} by the zero-profit condition \eqref{eq:lender_zp_compact}, the equilibrium lending rate satisfies:
\begin{equation}\label{eq:efp}
Z_t = \Rstar \cdot \underbrace{\frac{\bar{\omega}_t}{\Gamma(\bar{\omega}_t) - \mu G(\bar{\omega}_t)}}_{\text{external finance premium}}.
\end{equation}
The ratio $Z_t / \Rstar$ exceeds unity whenever $\bar{\omega}_t > 0$ and is increasing in $\bar{\omega}_t$.

Dividing the intermediary FOC \eqref{eq:int_foc} by the zero-profit condition \eqref{eq:lender_zp_compact} and substituting \eqref{eq:efp}, the threshold $\bar{\omega}_t$ is pinned down by the leverage ratio alone:
\begin{equation}\label{eq:omega_leverage}
1 - \Gamma(\bar{\omega}_t) = \Gamma'(\bar{\omega}_t)\,\bar{\omega}_t \cdot \frac{N_t}{ \Mf_t - N_t}.
\end{equation}
For given $\Mf_t$, a decrease in $N_t$ raises leverage and increases $\bar{\omega}_t$. \\

Solving the zero-profit condition \eqref{eq:lender_zp_compact} for $p_{m,t}$ yields the import price equation:
\begin{equation}\label{eq:pm}
p_{m,t} =  \Rstar \cdot \underbrace{\left(1 - \frac{N_t}{ M^f_t}\right)}_{\text{leverage}} \cdot \underbrace{\frac{1}{\Gamma(\bar{\omega}_t) - \mu G(\bar{\omega}_t)}}_{\text{CSV friction}}.
\end{equation}

In order to prevent friction in the household's Period 0 consumption, and form a baseline for Period 1 allocations, I impose the following assumption:
\begin{assumption} \label{ass:p0_capitalisation}
    Intermediaries are sufficiently well capitalised in Period 0 that the external finance premium is negligible; $p_{m,0} \approx  \Rstar$.
\end{assumption}

\subsection{Household Intratemporal Optimality}

The first-order conditions with respect to $\md_t$ and $\mf_t$ from the CES aggregator \eqref{eq:CES} yield the standard intratemporal demand function:
\begin{equation}\label{eq:mf_demand}
\mf_t = \md_t \left(\frac{1-\alpha}{\alpha\, p_{m,t}}\right)^{\!\frac{1}{1-\eta}},
\end{equation}
and the shadow value of income:
\begin{equation}\label{eq:shadow}
\lambda_t = u'(C_t)\,\frac{\partial C_t}{\partial \md_t} = u'(C_t)\,\alpha\!\left(\frac{C_t}{\md_t}\right)^{\!1-\eta}.
\end{equation}

\subsection{Optimal Default}

\begin{lemma}[Optimal Default Policy]\label{lem:default}
The household's first-order condition with respect to $D \in [0, b_1]$ is:
\begin{equation}\label{eq:foc_D}
\frac{\partial \mathcal{L}_1}{\partial D} = \lambda_1\!\left(1 - \mf_1 \frac{\partial p_{m,1}}{\partial D}\right).
\end{equation}
The marginal benefit of an additional unit of default is one unit of budget relief. The marginal cost is the induced increase in the domestic import price, weighted by import demand. The full Karush--Kuhn--Tucker conditions are:
\begin{equation}\label{eq:KKT}
\begin{cases}
D = 0 & \text{if } 1 \leq \mf_1 \dfrac{\partial p_{m,1}}{\partial D}\bigg|_{D=0} \quad \text{\emph{(no default)}},\\[10pt]
1 = \mf_1 \dfrac{\partial p_{m,1}}{\partial D} & \text{if } D \in (0, b_1) \quad \text{\emph{(partial default)}},\\[10pt]
D = b_1 & \text{if } 1 \geq \mf_1 \dfrac{\partial p_{m,1}}{\partial D}\bigg|_{D=b_1} \quad \text{\emph{(full default)}}.
\end{cases}
\end{equation}
At an interior solution, the household equates the marginal budgetary gain from one extra unit of default with the marginal cost through the external finance premium.
\end{lemma}

\subsection{Transmission of Default to Import Prices}

The mechanism by which sovereign default raises import prices, our key transmission process of interest, can be traced through the intermediary balance sheet. From the net-worth equation \eqref{eq:nw1}:
\begin{equation}\label{eq:dpm_dD}
\frac{\partial p_{m,1}}{\partial D} = -\gamma \frac{\partial p_{m,1}}{\partial N_1}.
\end{equation}
An increase in $D$ erodes intermediary net worth, raising leverage, pushing up the default threshold, increasing the external finance premium, and passing through to the import price:
\[
D \uparrow \;\xrightarrow{\eqref{eq:nw1}}\; N_1 \downarrow \;\xrightarrow{\eqref{eq:omega_leverage}}\; \bar{\omega}_1 \uparrow \;\xrightarrow{\eqref{eq:efp}}\; \frac{Z_1}{\Rstar} \uparrow \;\xrightarrow{\eqref{eq:pm}}\; p_{m,1} \uparrow \;\xrightarrow{\eqref{eq:mf_demand}}\; \mf_1 \downarrow \;\Longrightarrow\; C_1 \downarrow.
\]

Differentiating \eqref{eq:pm} with respect to $N_1$ at fixed $\Mf_1$:
\begin{equation}\label{eq:dpm_dn}
\frac{\partial p_{m,1}}{\partial N_1} =  \Rstar \cdot \frac{-\dfrac{1}{ \Mf_1}\bigl[\Gamma(\bar{\omega}_1) - \mu G(\bar{\omega}_1)\bigr] - \left(1 - \dfrac{N_1}{ \Mf_1}\right)\!\bigl[\Gamma'(\bar{\omega}_1) - \mu G'(\bar{\omega}_1)\bigr]\dfrac{\partial \bar{\omega}_1}{\partial N_1}}{\bigl[\Gamma(\bar{\omega}_1) - \mu G(\bar{\omega}_1)\bigr]^2}.
\end{equation}
This is strictly negative. The first term in the numerator captures the direct reduction in leverage; the second captures the indirect effect through the lowering of $\bar{\omega}_1$, which reduces expected auditing costs. The denominator $[\Gamma - \mu G]^2$ is the source of convexity in the default penalty: as net worth falls in default and $\bar{\omega}$ rises, $\Gamma - \mu G$ shrinks, causing the denominator to contract and the magnitude of $\partial p_{m,1}/\partial N_1$ to accelerate.

To complete the derivation, implicitly differentiating \eqref{eq:omega_leverage} with respect to $N_1$ at fixed $\Mf_1$:
\begin{equation}\label{eq:domega_dn}
\frac{\partial \bar{\omega}_1}{\partial N_1} = \frac{-\Gamma'(\bar{\omega}_1)\,\bar{\omega}_1 \cdot \dfrac{ \Mf_1}{( \Mf_1 - N_1)^2}}{\Gamma'(\bar{\omega}_1) + \bigl[\Gamma''(\bar{\omega}_1)\,\bar{\omega}_1 + \Gamma'(\bar{\omega}_1)\bigr]\frac{N_1}{M^f_1-N_1}},
\end{equation}
which is strictly negative provided the second-order conditions of the intermediary's problem are satisfied. Higher net worth lowers the default threshold. The numerator is negative because $\Gamma' > 0$ and $\bar{\omega} > 0$; the denominator is positive by the second-order conditions.

\begin{proposition}[Convexity of the Default Penalty]\label{prop:convexity}
The penalty to the Representative Household of default is convex in $D$: a linear increase in sovereign default triggers a more-than-proportional increase in the domestic import price $p_{m,1}$. This follows from two reinforcing effects as leverage increases:
\begin{enumerate}[label=(\roman*)]
\item $|\partial\bar{\omega}_t / \partial N_t|$ grows, since the numerator of \eqref{eq:domega_dn} expands via the $( \Mf_t - N_t)^2$ term while the denominator contracts;
\item $[\Gamma(\bar{\omega}_t) - \mu G(\bar{\omega}_t)]^2$ in the denominator of \eqref{eq:dpm_dn} shrinks as $\bar{\omega}_t$ rises.
\end{enumerate}
Together, $\partial p_{m,1}/\partial D$ is increasing in $D$.
\end{proposition}

% Worth stating here that, whilst convexity pushes against total default, it does not rule it out.

\begin{proposition}[Default increases in the ratio of debt-to-endowment]\label{prop:inv-debt-gdp}
Assume an interior default equilibrium where $D\in(0,b_1)$ and the second-order condition for utility maximization is strictly satisfied. The optimal sovereign default volume $D(y_1, b_1)$ is:
\begin{enumerate}[label=(\roman*)]
    \item Strictly decreasing in the realised Period 1 endowment $y_1$.
    \item Strictly increasing in the Period 1 debt issuance $b_1$.
\end{enumerate}
Consequently, the optimal haircut is governed by the household's capacity to pay, increasing alongside the debt-to-endowment ratio $b_1/y_1$.
\begin{proof}
    Let $F(D;y_1,b_1)$ denote the first-order condition for optimal default \eqref{eq:KKT}, under an interior equilibrium. Also, let $W_1\equiv y_1-(b_1-D)+\Pi_1$ denote the household's Period 1 wealth. By Proposition \ref{prop:convexity}, the derivative of $F(.)$ the  with respect to $D$ is strictly negative. Applying the Implicit Function Theorem, the comparative statics of optimal default with respect to the state variable $y_1$ is given by
    \begin{equation*}
        \frac{\partial F(D;y_1,b_1)}{\partial y_1}=-\left( \frac{\partial m^f_1}{\partial W_1} \frac{\partial W_1}{\partial y_1} \right)\frac{\partial p_{m,1}}{\partial D}.
    \end{equation*}
    Since $\frac{\partial W_1}{\partial y_1}=1$, $\frac{\partial p_{m,1}}{\partial D}>0$ and, as $\eta<0$, $\frac{\partial m^f_1}{\partial W_1}>0$, it follows that $\frac{\partial F(D;y_1,b_1)}{\partial y_1}<0$. Therefore $\frac{\partial D}{\partial y_1}<0$.

    Differentiating $F(.)$ with respect to $b_1$ yields
    \begin{equation*}
        \frac{\partial F(D;y_1,b_1)}{\partial b_1} = -\left( \frac{\partial m^f_1}{\partial W_1} \frac{\partial W_1}{\partial b_1} \right)\frac{\partial p_{m,1}}{\partial D}+m^f_1\left( \frac{\partial}{\partial b_1} \frac{\partial p_{m,1}}{\partial D} \right).
    \end{equation*}
    Due to the construction of claims made in Period 0, $\frac{\partial W_1}{\partial b_1}=-1$, in turn guaranteeing $\frac{\partial m^f_1}{\partial b_1}<0$. As $b_1$ enters positively into the Domestic Intermediary's Period 1 net-worth \eqref{eq:bc1}, from \eqref{eq:domega_dn} we can see that $\frac{\partial}{\partial b_1}\frac{\partial p_{m,1}}{\partial D}<0$. These two derivatives mean that $\frac{\partial F}{\partial b_1}>0$, implying $\frac{\partial D}{\partial b_1}>0$.
\end{proof}

\end{proposition}

Proposition \ref{prop:convexity} in isolation produces the nonlinearity in default penalty necessary to produce the type of "doom-loop" transmission in bank balance-sheet erosion and sovereign default we witness empirically. Combining with Proposition \ref{prop:inv-debt-gdp} induces over-borrowing consistent with debt-overhang; a comparative static formalisation of this can be found in Section \ref{sec:implications}.

\subsection{Intertemporal Optimality}

\begin{lemma}[Euler Equation]\label{lem:euler}
The household's first-order condition with respect to $b_1$, applying the envelope theorem to $V_1$, yields:
\begin{equation}\label{eq:euler}
\lambda_0\, q_0 = \beta\,\E_0\!\left[\lambda_1\!\left(1 + \gamma\,\mf_1 \frac{\partial p_{m,1}}{\partial N_1}\right)\right].
\end{equation}
\end{lemma}

\begin{proof}
By the envelope theorem, the marginal value of an additional unit of debt carried into Period 1 is:
\[
\frac{\partial V_1}{\partial b_1} = \lambda_1\!\left(-1 - \mf_1 \frac{\partial p_{m,1}}{\partial b_1}\right).
\]
Since $N_1 = \bar{n} + \gamma(b_1 - D)$ and default $D$ is taken as given at the time of issuance:
\[
\frac{\partial p_{m,1}}{\partial b_1} = \gamma \frac{\partial p_{m,1}}{\partial N_1}.
\]
Note the sign: higher $b_1$ raises intermediary net worth (since banks hold $\gamma b_1$ in bonds), so $\partial p_{m,1}/\partial b_1 < 0$. Combining with the Period 0 first-order condition $\lambda_0 q_0 = \beta \E_0[-\partial V_1 / \partial b_1]$ and simplifying yields \eqref{eq:euler}.
\end{proof}

The left-hand side of \eqref{eq:euler} is the marginal utility cost of purchasing one unit of debt at price $q_0$ in Period 0. The right-hand side comprises two components: the direct repayment of one unit of resources, and the improvement in Period 1 import prices from the additional net worth that $\gamma$ units of bond holdings deliver to intermediaries. Since $\partial p_{m,1}/\partial N_1 < 0$, the term $\gamma \mf_1 (\partial p_{m,1}/\partial N_1)$ is negative. Higher debt issuance strengthens bank balance sheets but also increases the household's future repayment burden. In equilibrium, the household balances the Period 0 consumption benefit of additional borrowing against both the direct repayment cost and the indirect effect on import prices.

%========================================================================
\section{Characterisation of Equilibrium} \label{sec:chareq}
%========================================================================

\subsection{Period 1 Equilibrium}

Take as given the states $(y_1, b_1)$ and the parameter $R^*$. 
Define the following shorthand, which depend only on 
$(D, \bar{\omega}_1, M^f_1)$ and parameters:
\begin{align*}
N_1(D) &\equiv \bar{n} + \gamma(b_1 - D), \\
\ell_1(D, M^f_1) &\equiv 1 - \frac{N_1(D)}{M^f_1}, \\
\Psi(\bar{\omega}_1) &\equiv \Gamma(\bar{\omega}_1) - \mu G(\bar{\omega}_1), \\
p_{m,1}(D, \bar{\omega}_1, M^f_1) &= R^* \cdot 
  \frac{\ell_1}{\Psi(\bar{\omega}_1)}.
\end{align*}
The Period~1 equilibrium values of $(D, \bar{\omega}_1, M^f_1)$ 
solve the following nonlinear system.

\medskip
\textit{Leverage--threshold condition} 
[from \eqref{eq:omega_leverage} and \eqref{eq:nw1}]:
\begin{equation}\label{eq:sys_leverage}
1 - \Gamma(\bar{\omega}_1) 
= \Gamma'(\bar{\omega}_1)\,\bar{\omega}_1 
  \cdot \frac{N_1(D)}{M^f_1 - N_1(D)}.
\end{equation}

\textit{Foreign input market clearing} 
[from \eqref{eq:mf_demand}, \eqref{eq:bc1}, 
\eqref{eq:mc_foreign}, and \eqref{eq:Pi_agg}]:
\begin{equation}\label{eq:sys_clearing}
M^f_1 \bigl[1 - \mu G(\bar{\omega}_1)\bigr]
\left[
  \left(\frac{\alpha\, p_{m,1}}{1 - \alpha}\right)^{\!\sigma} 
  + p_{m,1}
\right]
= y_1 - (b_1 - D) 
  + \bigl[1 - \Gamma(\bar{\omega}_1)\bigr]\, p_{m,1}\, M^f_1.
\end{equation}

\textit{Interior default condition} 
[from \eqref{eq:KKT}, \eqref{eq:dpm_dD}, 
and \eqref{eq:dpm_dn}]:
\begin{equation}\label{eq:sys_default}
\Psi(\bar{\omega}_1)^2 
= \gamma R^* M^f_1 \bigl[1 - \mu G(\bar{\omega}_1)\bigr]
\left(
  \frac{\Psi(\bar{\omega}_1)}{M^f_1}
  + \ell_1 
    \Psi'(\bar{\omega}_1)
    \left\lvert
      \frac{\partial \bar{\omega}_1}{\partial N_1}
    \right\rvert
\right),
\end{equation}
where
\begin{equation*}
\frac{\partial \bar{\omega}_1}{\partial N_1}
= \frac{
  -\Gamma'(\bar{\omega}_1)\,\bar{\omega}_1\, M^f_1
}{
  (M^f_1 - N_1)
  \Bigl[
    \Gamma'(\bar{\omega}_1)(M^f_1 - N_1)
    + N_1 \bigl[\Gamma''(\bar{\omega}_1)\,\bar{\omega}_1 
      + \Gamma'(\bar{\omega}_1)\bigr]
  \Bigr]
}.
\end{equation*} \\

At corner solutions, \eqref{eq:sys_default} is replaced by $D = 0$ or $D = b_1$ with the corresponding inequality 
from the KKT conditions \eqref{eq:KKT}. \\

All other Period~1 variables are determined residually: $N_1$ from 
\eqref{eq:nw1}, $p_{m,1}$ from \eqref{eq:pm}, $m^f_1$ from \eqref{eq:mc_foreign}, $\Pi_1$ from \eqref{eq:Pi_agg}, $m^d_1$ from \eqref{eq:bc1}, $C_1$ from \eqref{eq:CES}, $Z_1$ from \eqref{eq:efp}, and $K_1 = M^f_1 - N_1$. \\

\subsection{Period 0 Equilibrium}

Given Period 1 policy functions $D(y_1,b_1)$, and the associated Period 1 equilibrium mappings, the Period 0 equilibrium values of $(b_1, q_0)$ solve the following system. \\

\textit{Euler equation} [from \eqref{eq:euler}]:
\begin{equation}
\lambda_0\, q_0 = \beta\,\E_0\!\left[\lambda_1\!\left(1 + \gamma\,\mf_1 \frac{\partial p_{m,1}}{\partial N_1}\right)\right],
\end{equation}
where $\lambda_t$ is derived in \eqref{eq:shadow}.\\

\textit{Intertemporal bond pricing equation} [from \eqref{eq:bondprice}]:
\begin{equation}
    q_0 = \frac{1}{\Rstar}\,\E_0\!\left[1 - \frac{D(y_1, b_1)}{b_1}\right].
\end{equation}

Given a solution, the remaining Period~0 objects are recovered as: $N_0$ from \eqref{eq:nw0}, $\mf_0$ from 
\eqref{eq:mf_demand}, $\md_0$ from \eqref{eq:bc0}, $C_0$ from \eqref{eq:CES}, $\Pi_0$ from 
\eqref{eq:Pi_agg}, and $K_0 = M^f_0 - N_0$. Under Assumption \ref{ass:p0_capitalisation}, $\bar{\omega}_0$ and $Z_0$ are pinned down by \eqref{eq:omega_leverage} and \eqref{eq:efp} at negligible values of the external finance premium.

\paragraph{Ruling out no-trade equilibrium} For the rest of the thesis, attention will be restricted to the non-trivial interior partial default equilibrium, in which $q_0>0$ and $D\in (0,b_1)$;

\begin{assumption}\label{ass:interior}
Parameters $(\bar{n}, \gamma, \sigma_\omega, \mu, \eta, \alpha, R^*)$ and states $(y_1, b_1)$ are such that the KKT conditions~\eqref{eq:KKT} admit an interior solution $D \in (0, b_1)$.
\end{assumption}

The model admits a second class of equilibria in which the international lender anticipates full default, sets $q_0=0$, and the household is indifferent between not borrowing and borrowing for free with the intention of defaulting upon all claims, as identified by \citet{dubey_default_2005} in models of default with non-contingent debt. The two-period setting presented in this model, without a continuation value from market access, means that the household is exactly indifferent between these two equilibria. I choose to omit the analysis of such an equilibrium, following the practice of \citet{arellano_default_2008}, \citet{peiris_capital_2025} and others, to focus upon the borrowing, default, and intermediary channels that are of primary interest to this thesis.


%========================================================================
\section{Comparative Statics}\label{sec:implications}
%=======================================================================

The competitive equilibrium of Definition~\ref{def:equil} features a pecuniary externality: the atomistic household treats the bond price $q_0$ parametrically and therefore does not internalise how its borrowing affects expected default and the cost of debt. To characterise this inefficiency, I define a constrained Ramsey planner's problem, under which there is no coordination failure and thus the effect of default on the cost of borrowing is fully internalised in allocation choices, and compare outcomes with the competitive equilibrium of Definition~\ref{def:equil}. 

I then go on to analytically demonstrate that the intermediaries' exposure to domestic sovereign debt, $\gamma$, acts as the primary structural parameter governing amplification of default severity, with the idiosyncratic risk shock, $\sigma_{\omega}$, as the driver of financial fragility.

\subsection{Welfare in Borrowing}

\paragraph{The Constrained Planner's Problem}\label{sec:planner}

Consider a domestic Ramsey planner who chooses $b_1$ in Period~0 to maximise household welfare, subject to the same Period~1 equilibrium conditions as the competitive economy. That is, the planner takes as given the Period~1 default rule $D(y_1, b_1)$ and the associated competitive equilibrium mappings for $(\bar{\omega}_1, M^f_1, p_{m,1}, C_1)$, but internalises the bond price schedule.
The planner solves:
\begin{equation}\label{eq:planner}
    \max_{b_1 \geq 0} \; u\!\bigl(C_0(b_1)\bigr) + \beta\,\E_0\!\bigl[u\!\bigl(C_1(y_1, b_1)\bigr)\bigr],
\end{equation}
\[
    m^d_0 = y_0 - b_0 + q_0(b_1)\cdot b_1 + \Pi_0.
\]

\begin{definition}[Constrained Planner's Equilibrium]\label{def:planner_equil}
    A constrained planner's equilibrium is an allocation $\{b_1^{P}, q_0^{P}, D^{P}(y_1)\}$ and associated prices and quantities such that:
    \begin{enumerate}[label=(\roman*)]
        \item $b_1^{P}$ solves the planner's problem \eqref{eq:planner};
        \item For each realisation $y_1$, the Period~1 equilibrium $(D, \bar{\omega}_1, M^f_1)$ satisfies the same system \eqref{eq:sys_leverage}--\eqref{eq:sys_default} as under the competitive equilibrium;
        \item The bond price satisfies the \textit{schedule} \eqref{eq:bondprice}.
    \end{enumerate}
\end{definition}

Whilst the planner's problem is identical to that of the atomistic household in Period 1, the critical distinction from the competitive equilibrium is that the planner perceives the total revenue from bond issuance as
\[
    \mathcal{R}(b_1) \equiv q_0(b_1)\cdot b_1,
\]
and therefore the marginal revenue from issuing an additional unit of debt is
\begin{equation}\label{eq:marginal_revenue}
    \mathcal{R}'(b_1) = q_0(b_1) + q_0'(b_1)\cdot b_1,
\end{equation}
where the competitive household perceives only the first term. The second term, $q_0'(b_1)\cdot b_1$, captures the debt-dilution externality: additional borrowing raises expected default, depresses the bond price, and erodes the revenue raised on \emph{all} outstanding issuance.


\paragraph{The Welfare Wedge}\label{sec:wedge}

\begin{proposition}[Overborrowing under CSV-Constrained Partial Default]\label{prop:overborrowing}
Let $(b_1^{CE}, D^{CE})$ denote the competitive equilibrium allocation of Definition~\ref{def:equil} and $(b_1^{P}, D^{P})$ the constrained planner's allocation of Definition~\ref{def:planner_equil}. Suppose the equilibrium features interior partial default, $D \in (0, b_1)$, as guaranteed by Assumption~\ref{ass:interior}. Then
\[
    b_1^{CE} > b_1^{P}:
\]
the competitive household over-borrows relative to the constrained planner's optimum.
\end{proposition}

\begin{proof}
Differentiating the planner's objective \eqref{eq:planner} with respect to $b_1$ yields the first-order condition
\begin{equation}\label{eq:planner_foc}
    \lambda_0^{P}\,\mathcal{R}'(b_1) = \beta\,\E_0\!\left[\lambda_1\!\left(1 + \gamma\,m^f_1\,\frac{\partial p_{m,1}}{\partial N_1}\right) + u'(C_1)\,\frac{\partial C_1}{\partial D}\,\frac{\partial D}{\partial b_1}\right],
\end{equation}
where $\lambda_t$ is the shadow value of income \eqref{eq:shadow} and $\mathcal{R}(b_1) \equiv q_0(b_1)\,b_1$ is total bond revenue, so that $\mathcal{R}'(b_1) = q_0(b_1) + q_0'(b_1)\,b_1$. The competitive household's Euler equation \eqref{eq:euler} satisfies
\[
    \lambda_0\,q_0 = \beta\,\E_0\!\left[\lambda_1\!\left(1 + \gamma\,m^f_1\,\frac{\partial p_{m,1}}{\partial N_1}\right)\right].
\]
Evaluating \eqref{eq:planner_foc} at the competitive allocation (so that $\lambda_0^{P} = \lambda_0$) and subtracting the Euler equation identifies the welfare wedge
\begin{equation}\label{eq:wedge}
    \underbrace{\lambda_0\,q_0'(b_1)\cdot b_1}_{\text{debt-dilution externality}} + \beta\,\E_0\!\left[\underbrace{u'(C_1)\,\frac{\partial C_1}{\partial D}\,\frac{\partial D}{\partial b_1}}_{\text{insurance value of default}}\right].
\end{equation}
At any interior partial-default solution, the household's first-order condition \eqref{eq:foc_D} implies $\partial C_1/\partial D = 0$, so the insurance term vanishes and \eqref{eq:wedge} reduces to its first component. Since higher debt raises expected default and depresses the bond price, $q_0'(b_1) < 0$, the wedge is strictly negative. The planner therefore values an additional unit of $b_1$ strictly less than the competitive household at the competitive allocation, and so optimally chooses $b_1^{P} < b_1^{CE}$. \\
\end{proof}

\begin{remark}\label{rem:corner}
It is worth noting that this does not necessarily hold in corner solutions: the envelope condition from \eqref{eq:foc_D} does not bind, and the sign of the second term of \eqref{eq:wedge}, and thus the direction of borrowing compared to the planner's optimum depends on the magnitude of the CSV friction relative to the intermediary net-worth.\\
\end{remark}

The wedge \eqref{eq:wedge} admits a natural interpretation. We can think of partial default, under incomplete markets, as expanding the effective asset span of the non-contingent bond. With partial default, the household can smooth its state-contingent repayment, making the non-contingent bond behave more like a portfolio of Arrow securities. The more responsive $D(y_1,b_1)$ is to the state, the better the insurance properties of the debt instrument. Under the CSV friction, however, households are subject to a convex cost associated with this insurance and at an interior optimum the household equates the marginal benefit and marginal cost so that the insurance collapses and isolates the debt-dilution externality as the sole source of the wedge. The result is over-borrowing. However, with a large enough risk-shock, there is no restriction on the magnitude of this term; the insurance term can dominate the debt-dilution externality, flipping the sign of the wedge and rationalising \textit{under-borrowing} relative to the planner.

\subsection{Amplification in Domestic Bank Sovereign Debt Exposure}\label{sec:comp_stat_gamma}

As discussed in Section \ref{sec:intermediary}, the comparative static in $\gamma$ isolates the role of domestic bank exposure to sovereign debt. Since $\bar n(\gamma)+\gamma b_0\equiv \bar A$, changes in $\gamma$ should not be interpreted as changes in the size of the banking sector, rather as changes in the composition of intermediary portfolios toward domestic sovereign claims.
 
Sovereign debt exposure governs the sensitivity of the cost of default to the CSV friction through \eqref{eq:pm}, via \eqref{eq:nw1}: $\partial N_1/\partial D = -\gamma$. Higher $\gamma$ amplifies the pass-through from default to intermediary net worth erosion, raising the external finance premium and import price, generating stronger import compression and larger consumption losses conditional on any given haircut.\footnote{The effect of $\gamma$ on the equilibrium choice of haircut severity is discussed in Section~\ref{sec:discussion}; the focus here is the conditional amplification channel from a given haircut.}

This is an intensive-margin result. In an analogous binary-default formulation of this model, $\gamma$ would affect the cost of the household switching from repayment to default, but it would not characterise how the marginal cost curve of default grows in steepness and convexity with the size of the haircut. Thus, under partial default we can quantitatively map import prices and consumption to observed haircuts.

% TODO: Composite figure with all five panels, or a summary table
% showing the direction and magnitude of each object's response to gamma.

\subsection{The Role of Idiosyncratic Banking Risk}\label{sec:comp_stat_sigma_omega}

The idiosyncratic productivity shock variance $\sigma_\omega^2$ is the primitive driver of financial fragility in this model. Following \citet{christiano_risk_2014}, who establish that variations in the cross-sectional standard deviation of idiosyncratic productivity (the "risk shock") are the dominant driver of business-cycle fluctuations in financial variables, $\sigma_\omega$ feeds through to all key equilibrium objects of the model: the financial-friction wedge $\Psi(\bar\omega) \equiv \Gamma(\bar\omega) - \mu G(\bar\omega)$, the default threshold $\bar\omega$, the external finance premium $Z/R^*$, the import price $p_{m,1}$, and ultimately the household's optimal default policy $D(y_1, b_1)$.

The partial effects of $\sigma_\omega$ on the primitive CSV objects, at fixed $\bar\omega$, fall naturally from the log-normal specification (\ref{eq:omega_dist}), where an increase in $\sigma_\omega$ constitutes a mean-preserving spread of the idiosyncratic shock distribution:

\begin{enumerate}
    \item[(i)] $\partial \Gamma(\bar\omega) / \partial \sigma_\omega < 0$. The lender's expected revenue share falls: a wider distribution shifts mass into the default region $\omega < \bar\omega$ where the lender no longer collects $\bar\omega \cdot p_{m,t} m^f$ in full, and into the upper tail where the intermediary retains the residual surplus.
    \item[(ii)] $\partial (\mu G(\bar\omega)) / \partial \sigma_\omega > 0$. Expected auditing costs rise, as more probability mass falls below $\bar\omega$ and triggers the deadweight monitoring loss.
    \item[(iii)] $\partial \Psi(\bar\omega) / \partial \sigma_\omega = \partial \Gamma / \partial \sigma_\omega - \partial(\mu G) / \partial \sigma_\omega < 0$. The net surplus accruing to the lender per unit of intermediated imports unambiguously falls.
\end{enumerate}

From (\ref{eq:pm}), we can see that, via result (iii), increases in $\sigma_{\omega}$ raises $p_{m,1}$ for any given leverage. Of more interest, the convexity of the import-price response in $D$, captured by the $\Psi(\bar\omega)^2$ denominator in (\ref{eq:dpm_dn}), intensifies in $\sigma_\omega$: as $\Psi$ shrinks, the same haircut produces a sharper net-worth-to-import-price pass-through. Idiosyncratic banking risk, in addition to shifting the equilibrium, increases curvature of the household's marginal cost-curve in default and acts as a exogenous commitment device for the household.


%========================================================================
\section{Quantitative Analysis} \label{sec:quantitative}
%========================================================================


I now move to examine the quantitative implications of the model by conducting numerical simulations. I have chosen to use Sri Lanka's 2021-2022 default period as a calibration anchor. Sri Lanka's recent and well-documented renegotiation with bilateral and multilateral creditors makes their default a prime candidate to simulate via a partial-default model. That being said, moment-matching within a two-period setting is less credible than in an infinite-horizon case; rather, the quantitative analysis here serves the purposes of (i) demonstrating that the model admits a computable equilibrium with empirically reasonable values (ii) numerical demonstrations of the types of key comparative statics that would otherwise be challenging to derive analytically.

Under the model's two-period setting, each period is set to a length of five years. This setting seeks to strike a balance between temporal realism and calibration feasibility. Periods shorter than this length do not allow for a realistic time frame we would reasonably expect sovereign renegotiation to occur within. Five years allows Period 1 to capture equilibrium following complete conclusion of refinancing. On the other hand, longer period settings would lead to issues of liquidity in our chosen instrument of calibration - CDS Swaps. 5 year sovereign bond CDS contracts are generally more widely traded than 10 year, thus ensuring implied default probability is adequately captured in price data. Thus, the discount rate and risk-free rate are calibrated to their respective five year compounded values. For the remainder of the quantitative analysis, I set my utility function to a CRRA arrangement,
\begin{equation*}
    u(C_t)=\frac{C_t^{1-\sigma_u}}{1-\sigma_u},
\end{equation*}
where $\sigma_u$ is the coefficient of relative risk aversion.

The model is solved numerically through a nested optimisation architecture. The Period 0 equilibrium is recovered by maximising the household's lifetime value function over $b_1$, with the expectation approximated by a seven-node Gauss-Hermite quadrature. For each candidate $b_1$ and quadrature node $y_1$, the Period 1 equilibrium is solved for. $D^*(y_1, b_1)$ is found by maximising the household's Period 1 utility over $D \in [0, b_1]$. At each candidate $D$, the leverage--threshold condition (\ref{eq:omega_leverage}) is solved analytically for $M^f_1$ in terms of $\bar\omega_1$, leaving the foreign-input market-clearing condition (\ref{eq:mc_foreign}) as a single equation in $\bar\omega_1$ which is solved residually. The total derivative $\partial p_{m,1}/\partial N_1$ entering the Period 0 Euler equation is computed at the optimum $D^*$ via central finite differences on the inner solver.

\subsection{Baseline Calibration: The Case of Sri Lanka}

\input{baseline_calibration}

I chose to anchor the calibration via the expected haircut, $\E\left[ {D}/{b_1}\right]$, in the model to target the implied expected loss backed out of credit-default swap data. Specifically, I look at Sri Lankan 5 year CDS pricing data, with implied default probability generated from the standard ISDA model with an assumed recovery rate of 40\%. Following Sri Lanka's sovereign default episode in 2021-22, the average daily implied default probability rose to $\approx 78\%$, from $\approx 22\%$ the prior five years - resulting in an expected loss of $\approx0.468$. This expected loss serves as the primary empirical moment targeted by the model's expected haircut. Table \ref{tab:calibration} documents the baseline calibration to Sri Lankan variables during this episode of default.

\input{simul_summary}

The baseline calibration results, reported in Tables \ref{tab:period0_summary} and \ref{tab:period1_states}, shows a generated haircut above the targeted CDS-implied expected loss, though capturing a highly distressed default and credit environment consistent with the 2021--22 period in Sri Lanka. Likewise, the annualised spread generated overshoots peak Sri Lanka 5 Years USD / United States 5 Years Government Bond Spread in 2022 of $\approx 2500\text{ bps}$ by around 1000 points, yet again remains of the same order of magnitude as crisis-period spreads. \\

\input{simul_results}

Reflecting upon the transmission flow of the model, the model exhibits default that is strongly state-contingent. Haircut severity falls monotonically with the realised endowment: the sovereign defaults most in low-output states and least in high-output states. Of note, the default policy reaches a full-default corner in the worst endowment state and approaches a low-haircut repayment region in the best state. Under our baseline calibration, allocations span both crisis and near-repayment states within the same default rule.

Interestingly, when in an interior-default state, the sovereign adjusts its haircut to endogenously target a particular default threshold, holding import prices and external finance premiums close to a common level across states. This is a numerical consequence of the household's default policy (\ref{eq:KKT}): the sovereign chooses the haircut until the marginal budgetary gain from default equals the marginal import-price cost.

Finally, the baseline simulation confirms that larger haircuts do indeed generate greater import compression, lowering consumption in kind.

%========================================================================
\section{Discussion} \label{sec:discussion}
%========================================================================

\subsection{Testable Predictions}\label{sec:predictions}

The comparative statics of Section \ref{sec:implications} and analysis in Section \ref{sec:quantitative} admit a series of empirical predictions that can be taken to the data:

\paragraph{Prediction 1: Haircuts increase monotonically and with convexity in debt-to-GDP} 
\emph{In a cross-section of sovereign restructuring episodes, realised haircuts are positively associated with the pre-default debt-to-GDP ratio.} This is a standard prediction rationalised by existing models of partial default \citep{arellano_partial_2023, goodhart_debt_2018, peiris_capital_2025}, and the model proposed in this thesis continues to generate this convex debt-to-GDP relationship with default.
 
\paragraph{Prediction 2: Import compression is graded in haircut severity}
\emph{Across restructuring episodes, larger realised haircuts should be associated with larger contractions in imports, especially in economies where imported inputs are difficult to substitute with domestic production.} Whilst \citet{mendoza_general_2012} document the relationship between default and import-based financial frictions, the friction is still generated via a binary market-exclusion channel; here, I propose an endogenous channel where import compression rises continually, and nonlinearly, in haircut.
 
\paragraph{Prediction 3: The haircut-import elasticity is increasing in domestic bank sovereign exposure}
\emph{The elasticity of imports with respect to haircut severity is larger in countries with greater domestic bank exposure to sovereign debt.} The doom-loop literature \citep{sosa-padilla_sovereign_2018, brunnermeier_sovereign-bank_2016} establishes that sovereign distress propagates to the financial sector, but does not deliver a graded cross-sectional prediction tied to a structural exposure parameter. By isolating $\gamma$ as the share of sovereign losses transferred to intermediaries, the model proposed in this thesis generates a direct mapping from this exposure to the \textit{slope} of the haircut-import relationship.
 
%\paragraph{Prediction 4: Private external finance premia rise with haircut severity}
%\emph{Larger sovereign haircuts are followed by larger increases in private external borrowing costs, particularly for banks and import-dependent firms.}
 
\paragraph{Prediction 4: Output losses are convex in haircut severity}
\emph{The relationship between haircut severity and post-default output decline is nonlinear: larger haircuts is be associated with disproportionately larger output losses. This convexity is stronger in economies with higher domestic bank exposure to sovereign debt.} The increase in the curvature of this relationship in domestic bank exposure to sovereign debt cannot be rationalised without the modeling combination of bank net-worth erosion and partial default.

\subsection{Limitations and Further Research}

% Weakness: always default, 
% Realistics spreads in quant analysis should be reserved to infinite-time horizon model
% If banks hold a small enough share of sovereign debt, the pass-through coefficient scales the marginal cost down. As γ→0, the marginal cost vanishes — but so does the *channel*: defaulting doesn't hurt you because banks don't hold the debt. In the limit γ=0 the model degenerates to one with no transmission, and the household defaults fully (since there's no cost).
% Also, reduced form
% Discussion of assumptions (1&2)

The most obvious direction for future research from the theoretical framework posed in this thesis is to extend the two-period model to an infinite-horizon setting. This would enable the model to speak to debt-accumulation dynamics, transition paths post-default (allowing exploration of serial-default) and more sophisticated moments-matched calibrations to a panel of emerging economies. The kinks at the corners of the household's default function under continuous partial default, combined with a large state-space including both $(b_t,N_t)$, generates a high computational cost associated with numerical solutions; this should not be prohibitive, however.

Assumption \ref{ass:interior} rules out the no-trade corner and ensures interior bond-market participation, which in turn delivers the continuous default severity that is the model's central object of analysis. In the calibrated equilibrium, however, the sovereign defaults in every state of nature, with severity varying from near-full default in the worst endowment state to a low haircut in the best. Empirically, this is at odds with observed default frequencies in emerging-market panels, and as such the model speaks only to the intensive margin of default rather than to the extensive margin of \textit{when} default occurs. This is not a limitation of Assumption 1 in isolation: in an infinite-horizon extension, the continuation value would likely discipline the default decision sufficiently to generate repayment regions in sufficiently good states. In the two-period setting, the assumption binds more tightly than it would otherwise.

An infinite-horizon extension would also allow for the opportunity to discipline banking parameters $\gamma,\bar{n}$, which the equilibrium allocations are highly sensitive to, by using richer micro-level data. $\gamma$ in particular is reduced-form by construction and acts as a key structural parameter - endogenising intermediary portfolio choices, following \citet{farhi_deadly_2018} for example, may provide richer equilibrium dynamics by removing a free parameter. Whilst $\gamma$ is well-interpretable as the portfolio-adjustment towards or away from domestic sovereign debt, generated by home-bias or financial repression, the parameter loses this interpretation when set to zero; the household is no longer subject to the intermediary-mediated default penalty. Examination of default induced by the \textit{existence} of idiosyncratic risk, rather than sensitivity to risk, would necessitate reworking of this parameter. Finally, the cash-in-advance nominal set-up delivers nominal neutrality (Proposition \ref{prop:neutrality}) by construction; introducing nominal rigidities would fundamentally change the implications of the CSV transmission mechanism, and would allow for analysis of real exchange rate dynamics, following the work of \citet{na_twin_2018}.

\subsection{Conclusion}

The theoretical framework developed within this thesis seeks to reverse the canonical emphasis sovereign default-originating credit crises by embedding a costly state verification friction in the domestic intermediary sector, with pass-through of idiosyncratic risk shocks through to import prices. By allowing the sovereign to choose a continuous haircut, the model generates clear first and second-order empirical predictions regarding how the realised haircut interacts with import compression and consumption contractions driven by exposure of the banking system to sovereign default risk.

The model delivers three discrete results. First, the default penalty is convex in the haircut: each successive unit of default erodes intermediary net worth, raises the external finance premium through the CSV friction, and feeds into import prices with nonlinearity. This convexity rationalises the doom-loop transmission without recourse to multiple equilibria or sunspot selection. Second, the atomistic household over-borrows relative to the constrained Ramsey planner at any interior partial-default solution.  Third, the comparative statics in $\gamma$ identify domestic bank exposure to sovereign debt as the primary amplification channel: holding total intermediary balance sheet size fixed, higher exposure steepens the haircut-import elasticity, the external finance premium response, and the consumption loss conditional on any realised default. The Sri Lankan calibration confirms that these mechanisms operate at empirically reasonable magnitudes in a crisis-period economy.

%========================================================================
\newpage
\printbibliography
%========================================================================


\end{document}